---
title: "Moralized Language Predicts Hate Speech (Main Paper)"
author: KS
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{booktabs}
   - \usepackage{float}
   - \usepackage{longtable}
   - \usepackage{multirow}
   - \usepackage{siunitx}
output:
  pdf_document:
    toc: yes
    keep_tex: no
    number_sections: yes
---
```{r setup, include=FALSE}
library(tidyverse)
library(lme4)
library(texreg)
library(xtable)
library(broom)
library(broom.mixed)
library(lubridate)
library(wesanderson)
library(car)
library(furrr)
library(glmmTMB)
library(mgcv)
library(ranger)

options(xtable.comment = FALSE, width = 80, scipen = 999)
plan(multisession, workers = parallel::detectCores() / 2)
source("utils.R")
```

```{r paths}
inputPath  <- "C:/Users/Josh/OneDrive - The Pennsylvania State University/DS 340W/Data/"
splitPath  <- "C:/Users/Josh/OneDrive - The Pennsylvania State University/DS 340W/Data/split_output/"
graphPath  <- "C:/Users/Josh/OneDrive - The Pennsylvania State University/DS 340W/Data/Graphs/"
rdataPath  <- "C:/Users/Josh/OneDrive - The Pennsylvania State University/DS 340W/R Data/"
```

```{r load-data}
load_dataset <- function(path, label) {
  read_csv(path, show_col_types = FALSE) %>%
    mutate(UserID     = factor(UserID),
           SourceHate = factor(SourceHate),
           Dataset    = label)
}

df_list <- list(
  Politicians = load_dataset(paste0(inputPath, "df_politicians.csv"), "Politicians"),
  Newspeople  = load_dataset(paste0(inputPath, "df_newspeople.csv"),  "Newspeople"),
  Activists   = load_dataset(paste0(inputPath, "df_activists.csv"),   "Activists")
)

df_train <- list(
  Politicians = load_dataset(paste0(splitPath, "df_politicians_train.csv"), "Politicians"),
  Newspeople  = load_dataset(paste0(splitPath, "df_newspeople_train.csv"),  "Newspeople"),
  Activists   = load_dataset(paste0(splitPath, "df_activists_train.csv"),   "Activists")
)

df_test <- list(
  Politicians = load_dataset(paste0(splitPath, "df_politicians_test.csv"), "Politicians"),
  Newspeople  = load_dataset(paste0(splitPath, "df_newspeople_test.csv"),  "Newspeople"),
  Activists   = load_dataset(paste0(splitPath, "df_activists_test.csv"),   "Activists")
)

cat("Training set sizes:\n")
walk2(df_train, names(df_train), ~ cat(" ", .y, ":", nrow(.x), "rows\n"))
cat("Test set sizes:\n")
walk2(df_test,  names(df_test),  ~ cat(" ", .y, ":", nrow(.x), "rows\n"))
```

# Functions
```{r functions}
plot_ccdf_dfs <- function(df, selected, y_min = 0.001, y_max = 1,
                          label_fun_x = NA, legend_position = c(0.72, 0.72),
                          breaks = c(0.0001, 0.001, 0.01, 0.1, 0.25, 0.5, 1),
                          ordering = NULL, colors = NULL, label_x = "Moral Language",
                          xlim_n = NULL, grouping_var = NULL, rounding = 1) {
  df %>%
    mutate(!!grouping_var := fct_relevel(factor(get(grouping_var)), ordering)) %>%
    group_by(Dataset) %>%
    group_modify(~ ccdf(.x %>% pull(selected))) %>%
    arrange(x) %>%
    mutate(y = lag(y, default = 1)) %>%
    ungroup() %>%
    ggplot(aes(x = x, y = y, group = Dataset, color = Dataset)) +
    geom_line(size = 2) +
    scale_y_continuous(labels = as.character(breaks * 100), trans = "log10",
                       breaks = breaks, limits = c(y_min, y_max), expand = c(0, 0)) +
    scale_x_continuous() +
    scale_colour_manual(values = colors) +
    labs(y = "CCDF (%)", x = label_x) +
    theme(legend.direction = "vertical", legend.position = legend_position,
          legend.spacing.x = unit(0.1, "cm"), legend.spacing.y = unit(0.1, "cm")) +
    xlim(xlim_n)
}

vnames_list <- c(
  "(Intercept)"         = "Intercept",
  "TextComplexity"      = "Text Complexity",
  "MoralWords"          = "Moral Words",
  "MoralEmotionalWords" = "Moral-Emotional Words",
  "EmotionalWords"      = "Emotional Words",
  "WordCount"           = "Word Count",
  "QuoteTRUE"           = "Quote (binary)"
)
```

# CCDF Plots
```{r ccdf-plots}
ccdf_colors <- wes_palette("Darjeeling1")[3:1]
ccdf_breaks <- c(0.0001, 0.001, 0.01, 0.1, 1)
df_combined <- bind_rows(df_list)

plot_ccdf_moral <- plot_ccdf_dfs(
  df = df_combined, selected = "MoralWords", label_x = "Moral Words",
  ordering = names(df_list), colors = ccdf_colors, xlim_n = c(0, 9),
  y_min = 0.0001, breaks = ccdf_breaks, legend_position = c(0.3, 0.3),
  grouping_var = "Dataset"
) + scale_x_continuous(breaks = c(0, 2, 4, 6, 8)) + coord_cartesian(xlim = c(0, 9))

plot_ccdf_moralemo <- plot_ccdf_dfs(
  df = df_combined, selected = "MoralEmotionalWords",
  label_x = "Moral-Emotional Words", ordering = names(df_list),
  colors = ccdf_colors, xlim_n = c(0, 6), y_min = 0.0001,
  breaks = ccdf_breaks, legend_position = c(0.3, 0.3), grouping_var = "Dataset"
)

plot_ccdf_hpu <- plot_ccdf_dfs(
  df = df_combined %>%
    group_by(Dataset, UserID) %>%
    summarise(HpU = mean(ProportionOfHate), .groups = "drop"),
  selected = "HpU", label_x = "Mean Share of Hateful Replies (per User)",
  ordering = names(df_list), colors = ccdf_colors, xlim_n = c(0, 0.2),
  breaks = ccdf_breaks, legend_position = c(0.75, 0.75), grouping_var = "Dataset"
)

print(plot_ccdf_moral)
print(plot_ccdf_moralemo)
print(plot_ccdf_hpu)

ggsave(plot_ccdf_moral,    file = paste0(graphPath, "CCDF_moral_words_by_df.pdf"),
       width = 16, height = 12, units = "cm")
ggsave(plot_ccdf_moralemo, file = paste0(graphPath, "CCDF_moralemotional_words_by_df.pdf"),
       width = 16, height = 12, units = "cm")
ggsave(plot_ccdf_hpu,      file = paste0(graphPath, "CCDF_HpU_df.pdf"),
       width = 16, height = 12, units = "cm")
```

# Alternative Model Specifications
```{r sample-for-dev, include=FALSE}
# Set to NULL to use full training data.
DEV_SAMPLE <- NULL

df_train_sample <- if (!is.null(DEV_SAMPLE)) {
  map(df_train, ~ slice_sample(.x, n = min(DEV_SAMPLE, nrow(.x))))
} else {
  df_train
}

cat("Sample sizes used for model fitting:\n")
walk2(df_train_sample, names(df_train_sample),
      ~ cat(" ", .y, ":", nrow(.x), "rows\n"))
```

<!--
ZIBB was attempted but abandoned due to non-identifiable zero-inflation
component across all three datasets. The zero-inflation random effect variance
collapsed to near-zero for Newspeople, indicating structural zeros are not
present in the data. Plain beta-binomial used instead.
```{r zibb-commented}
fit_zibb <- function(data, name) {
  cat("\nFitting ZIBB:", name, "| n =", nrow(data),
      "| started:", format(Sys.time(), "%H:%M:%S"), "\n")
  start <- Sys.time()
  m <- tryCatch(
    glmmTMB(
      formula   = cbind(HReplies, Replies - HReplies) ~
                    MediaAttached + TextComplexity + MoralWords +
                    MoralEmotionalWords + EmotionalWords + WordCount +
                    Quote + (1 | UserID),
      ziformula = ~ MediaAttached + MoralWords + MoralEmotionalWords,
      data      = data,
      family    = betabinomial(link = "logit"),
      control   = glmmTMBControl(optCtrl = list(iter.max = 1e5, eval.max = 1e5))
    ),
    error = function(e) { cat("ERROR:", e$message, "\n"); NULL }
  )
  cat("Completed in", round(difftime(Sys.time(), start, units = "mins"), 2), "mins\n")
  m
}
zibb_models <- imap(df_train_sample, fit_zibb)
```
-->

## Model 1: Beta-Binomial
```{r bb-fit}
fit_bb <- function(data, name) {
  cat("\nFitting BB:", name, "| n =", nrow(data),
      "| started:", format(Sys.time(), "%H:%M:%S"), "\n")
  start <- Sys.time()

  m <- tryCatch(
    glmmTMB(
      formula = cbind(HReplies, Replies - HReplies) ~
                  MediaAttached + TextComplexity + MoralWords +
                  MoralEmotionalWords + EmotionalWords + WordCount +
                  Quote + (1 | UserID),
      data    = data,
      family  = betabinomial(link = "logit"),
      control = glmmTMBControl(optCtrl = list(iter.max = 1e5, eval.max = 1e5))
    ),
    error = function(e) { cat("ERROR:", e$message, "\n"); NULL }
  )

  cat("Completed in",
      round(difftime(Sys.time(), start, units = "mins"), 2), "mins\n")
  m
}

bb_models <- imap(df_train_sample, fit_bb)
save(bb_models, file = paste0(rdataPath, "bb_models.RData"))

cat("\n===== BB Summaries =====\n")
iwalk(bb_models, function(m, nm) {
  if (!is.null(m)) { cat("\n--", nm, "--\n"); print(summary(m)) }
})
```

## BB Cross-Validation
```{r bb-cv}
evaluate_bb_cv <- function(data, dataset_name, seed = 123) {

  cat("\nBB CV Evaluation:", dataset_name,
      "| n =", nrow(data), "\n")
  set.seed(seed)

  df <- data %>%
    mutate(
      .y_num   = HReplies,
      .y_denom = Replies - HReplies,
      .prop    = HReplies / Replies,
      UserID   = factor(UserID)
    ) %>%
    filter(!is.na(.prop), Replies > 0)

  user_ids <- levels(df$UserID)
  fold_map <- setNames(
    sample(rep(seq_len(5), length.out = length(user_ids))),
    user_ids
  )
  df$fold <- fold_map[as.character(df$UserID)]

  fold_metrics <- data.frame(fold = integer(0), rmse = numeric(0),
                              mae  = numeric(0), r2   = numeric(0),
                              loglik = numeric(0))

  for (k in seq_len(5)) {
    cat("  Fold", k, "| started:", format(Sys.time(), "%H:%M:%S"), "\n")

    train <- df[df$fold != k, ]
    test  <- df[df$fold == k, ]

    m_cv <- tryCatch(
      glmmTMB(
        formula = cbind(.y_num, .y_denom) ~
                    MediaAttached + TextComplexity + MoralWords +
                    MoralEmotionalWords + EmotionalWords + WordCount +
                    Quote + (1 | UserID),
        data    = train,
        family  = betabinomial(link = "logit"),
        control = glmmTMBControl(optCtrl = list(iter.max = 1e5, eval.max = 1e5))
      ),
      error = function(e) { cat("  ERROR fold", k, ":", e$message, "\n"); NULL }
    )
    if (is.null(m_cv)) next

    pred <- tryCatch(
      predict(m_cv, newdata = test, type = "response",
              allow.new.levels = TRUE),
      error = function(e) { cat("  Predict error fold", k, "\n"); NULL }
    )
    if (is.null(pred)) next

    pred   <- pmax(0, pmin(1, pred))
    actual <- test$.prop
    ss_res <- sum((actual - pred)^2,         na.rm = TRUE)
    ss_tot <- sum((actual - mean(actual))^2, na.rm = TRUE)
    rmse_k <- sqrt(mean((actual - pred)^2,   na.rm = TRUE))
    mae_k  <- mean(abs(actual - pred),        na.rm = TRUE)
    r2_k   <- 1 - ss_res / ss_tot
    ll_k   <- as.numeric(logLik(m_cv))

    cat("    RMSE:", round(rmse_k, 5),
        "| MAE:",   round(mae_k,  5),
        "| R2:",    round(r2_k,   4),
        "| logLik:", round(ll_k,  2), "\n")

    fold_metrics <- rbind(fold_metrics,
                          data.frame(fold = k, rmse = rmse_k,
                                     mae = mae_k, r2 = r2_k, loglik = ll_k))
  }

  cat("  ── BB CV Summary:", dataset_name, "──\n")
  cat("  Mean RMSE:", round(mean(fold_metrics$rmse), 5),
      "(SD:", round(sd(fold_metrics$rmse), 5), ")\n")
  cat("  Mean MAE :", round(mean(fold_metrics$mae),  5),
      "(SD:", round(sd(fold_metrics$mae),  5), ")\n")
  cat("  Mean R2  :", round(mean(fold_metrics$r2),   4),
      "(SD:", round(sd(fold_metrics$r2),   4), ")\n")

  list(fold_metrics = fold_metrics,
       mean_rmse    = mean(fold_metrics$rmse),
       mean_mae     = mean(fold_metrics$mae),
       mean_r2      = mean(fold_metrics$r2))
}

bb_cv_results <- list(
  Politicians = evaluate_bb_cv(df_train$Politicians, "Politicians"),
  Newspeople  = evaluate_bb_cv(df_train$Newspeople,  "Newspeople"),
  Activists   = evaluate_bb_cv(df_train$Activists,   "Activists")
)

save(bb_cv_results, file = paste0(rdataPath, "bb_cv_results.RData"))
cat("\nBB CV complete and saved.\n")
```

## Model 2: Generalized Additive Mixed Model
```{r gamm-fit}
get_k <- function(data, var, max_k = 10) {
  min(max_k, floor(length(unique(data[[var]])) / 2), 10)
}

fit_gamm <- function(data, name) {
  cat("\nFitting GAMM:", name, "| n =", nrow(data),
      "| started:", format(Sys.time(), "%H:%M:%S"), "\n")
  start <- Sys.time()

  k_vals <- sapply(
    c("TextComplexity", "MoralWords", "MoralEmotionalWords",
      "EmotionalWords", "WordCount"),
    get_k, data = data
  )
  cat("  k values:", k_vals, "\n")

  m <- tryCatch(
    gam(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached +
        s(TextComplexity,      k = k_vals["TextComplexity"]) +
        s(MoralWords,          k = k_vals["MoralWords"]) +
        s(MoralEmotionalWords, k = k_vals["MoralEmotionalWords"]) +
        s(EmotionalWords,      k = k_vals["EmotionalWords"]) +
        s(WordCount,           k = k_vals["WordCount"]) +
        Quote + s(UserID, bs = "re"),
      data   = data,
      family = binomial(link = "logit"),
      method = "REML"
    ),
    error = function(e) {
      cat("Smooth model failed:", e$message, "\nTrying linear fallback...\n")
      tryCatch(
        gam(
          cbind(HReplies, Replies - HReplies) ~
            MediaAttached + TextComplexity + MoralWords +
            MoralEmotionalWords + EmotionalWords + WordCount +
            Quote + s(UserID, bs = "re"),
          data = data, family = binomial(link = "logit"), method = "REML"
        ),
        error = function(e2) { cat("Fallback failed:", e2$message, "\n"); NULL }
      )
    }
  )

  cat("Completed in", round(difftime(Sys.time(), start, units = "mins"), 2), "mins\n")
  m
}

gamm_models <- imap(df_train_sample, fit_gamm)
save(gamm_models, file = paste0(rdataPath, "gamm_models.RData"))

cat("\n===== GAMM Smooth Term Summaries =====\n")
iwalk(gamm_models, function(m, nm) {
  if (!is.null(m)) {
    cat("\n--", nm, "--\n")
    print(summary(m)$s.table)
  }
})
```

## GAMM Cross-Validation
```{r gamm-cv}
evaluate_gamm_cv <- function(data, dataset_name, seed = 123) {

  cat("\nGAMM CV Evaluation:", dataset_name,
      "| n =", nrow(data), "\n")
  set.seed(seed)

  df <- data %>%
    mutate(UserID = factor(UserID),
           .prop  = HReplies / Replies) %>%
    filter(!is.na(.prop), Replies > 0)

  user_ids <- levels(df$UserID)
  fold_map <- setNames(
    sample(rep(seq_len(5), length.out = length(user_ids))),
    user_ids
  )
  df$fold <- fold_map[as.character(df$UserID)]

  fold_metrics <- data.frame(fold = integer(0), rmse = numeric(0),
                              mae  = numeric(0), r2   = numeric(0),
                              dev_expl = numeric(0))

  for (k in seq_len(5)) {
    cat("  Fold", k, "| started:", format(Sys.time(), "%H:%M:%S"), "\n")

    train <- df[df$fold != k, ]
    test  <- df[df$fold == k, ]

    k_vals <- sapply(
      c("TextComplexity", "MoralWords", "MoralEmotionalWords",
        "EmotionalWords", "WordCount"),
      get_k, data = train
    )
    cat("    k values:", k_vals, "\n")

    m_cv <- tryCatch(
      gam(
        cbind(HReplies, Replies - HReplies) ~
          MediaAttached +
          s(TextComplexity,      k = k_vals["TextComplexity"]) +
          s(MoralWords,          k = k_vals["MoralWords"]) +
          s(MoralEmotionalWords, k = k_vals["MoralEmotionalWords"]) +
          s(EmotionalWords,      k = k_vals["EmotionalWords"]) +
          s(WordCount,           k = k_vals["WordCount"]) +
          Quote + s(UserID, bs = "re"),
        data   = train,
        family = binomial(link = "logit"),
        method = "REML"
      ),
      error = function(e) {
        cat("    ERROR fold", k, ":", e$message, "\n")
        cat("    Trying linear fallback...\n")
        tryCatch(
          gam(
            cbind(HReplies, Replies - HReplies) ~
              MediaAttached + TextComplexity + MoralWords +
              MoralEmotionalWords + EmotionalWords + WordCount +
              Quote + s(UserID, bs = "re"),
            data = train, family = binomial(link = "logit"), method = "REML"
          ),
          error = function(e2) { cat("    Fallback ERROR:", e2$message, "\n"); NULL }
        )
      }
    )
    if (is.null(m_cv)) next

    pred <- tryCatch(
      predict(m_cv, newdata = test, type = "response",
              exclude = "s(UserID)"),
      error = function(e) { cat("    Predict error fold", k, "\n"); NULL }
    )
    if (is.null(pred)) next

    pred   <- pmax(0, pmin(1, pred))
    actual <- test$.prop
    ss_res <- sum((actual - pred)^2,         na.rm = TRUE)
    ss_tot <- sum((actual - mean(actual))^2, na.rm = TRUE)
    rmse_k <- sqrt(mean((actual - pred)^2,   na.rm = TRUE))
    mae_k  <- mean(abs(actual - pred),        na.rm = TRUE)
    r2_k   <- 1 - ss_res / ss_tot
    dev_k  <- summary(m_cv)$dev.expl

    cat("    RMSE:", round(rmse_k, 5),
        "| MAE:",    round(mae_k,  5),
        "| R2:",     round(r2_k,   4),
        "| Dev expl:", round(dev_k * 100, 2), "%\n")

    fold_metrics <- rbind(fold_metrics,
                          data.frame(fold = k, rmse = rmse_k, mae = mae_k,
                                     r2 = r2_k, dev_expl = dev_k))
  }

  cat("  ── GAMM CV Summary:", dataset_name, "──\n")
  cat("  Mean RMSE:", round(mean(fold_metrics$rmse), 5),
      "(SD:", round(sd(fold_metrics$rmse), 5), ")\n")
  cat("  Mean MAE :", round(mean(fold_metrics$mae),  5),
      "(SD:", round(sd(fold_metrics$mae),  5), ")\n")
  cat("  Mean R2  :", round(mean(fold_metrics$r2),   4),
      "(SD:", round(sd(fold_metrics$r2),   4), ")\n")
  cat("  Mean Dev:", round(mean(fold_metrics$dev_expl) * 100, 4), "%\n")

  list(fold_metrics = fold_metrics,
       mean_rmse    = mean(fold_metrics$rmse),
       mean_mae     = mean(fold_metrics$mae),
       mean_r2      = mean(fold_metrics$r2),
       mean_dev     = mean(fold_metrics$dev_expl))
}

gamm_cv_results <- list(
  Politicians = evaluate_gamm_cv(df_train$Politicians, "Politicians"),
  Newspeople  = evaluate_gamm_cv(df_train$Newspeople,  "Newspeople"),
  Activists   = evaluate_gamm_cv(df_train$Activists,   "Activists")
)

save(gamm_cv_results, file = paste0(rdataPath, "gamm_cv_results.RData"))
cat("\nGAMM CV complete and saved.\n")
```

## Model 3: Generalized Mixed Effects Random Forest
```{r gmerf-function}
fit_gmerf <- function(data,
                      dataset_name,
                      outcome_col   = "ProportionOfHate",
                      weight_col    = "Replies",
                      cluster_col   = "UserID",
                      predictors    = c("MediaAttached", "TextComplexity",
                                        "MoralWords", "MoralEmotionalWords",
                                        "EmotionalWords", "WordCount", "Quote"),
                      max_iter      = 20,
                      tol           = 1e-2,
                      num_trees     = 500,
                      min_node_size = 5,
                      seed          = 123) {

  cat("\n", rep("=", 55), "\n", sep = "")
  cat("GMERF:", dataset_name, "| n =", nrow(data),
      "| clusters =", length(unique(data[[cluster_col]])), "\n")
  cat(rep("=", 55), "\n", sep = "")

  set.seed(seed)

  df <- data
  for (p in predictors) {
    if (p %in% names(df) && is.logical(df[[p]])) df[[p]] <- as.numeric(df[[p]])
  }
  df[[".cluster"]] <- factor(df[[cluster_col]])
  df[[".weight"]]  <- df[[weight_col]]
  df[[".y"]]       <- df[[outcome_col]]

  keep <- c(".y", ".weight", ".cluster", predictors)
  df   <- df[complete.cases(df[, keep[keep %in% names(df)]]), ]

  cluster_id <- df[[".cluster"]]
  weights    <- df[[".weight"]] / mean(df[[".weight"]])
  y          <- df[[".y"]]

  b_hat     <- setNames(rep(0.0, length(levels(cluster_id))), levels(cluster_id))
  ll_prev   <- -Inf
  converged <- FALSE
  iter_log  <- data.frame(iter = integer(0), rf_oob_rmse = numeric(0),
                           re_var = numeric(0), resid_var = numeric(0),
                           log_lik = numeric(0), delta_ll = numeric(0))
  rf_model  <- NULL
  lmm_model <- NULL

  rf_formula <- as.formula(paste(".y_star ~", paste(predictors, collapse = " + ")))

  for (iter in seq_len(max_iter)) {

    cat("  Iter", iter, "|", format(Sys.time(), "%H:%M:%S"), "\n")

    b_vec              <- b_hat[as.character(cluster_id)]
    b_vec[is.na(b_vec)] <- 0
    rf_df              <- df[, predictors, drop = FALSE]
    rf_df[[".y_star"]] <- y - b_vec

    rf_model <- ranger(
      formula       = rf_formula,
      data          = rf_df,
      num.trees     = num_trees,
      min.node.size = min_node_size,
      importance    = "impurity",
      case.weights  = weights,
      seed          = seed,
      num.threads   = parallel::detectCores() - 1
    )

    f_hat <- predict(rf_model, data = rf_df)$predictions
    e_hat <- y - f_hat

    lmm_model <- tryCatch(
      suppressWarnings(
        lmer(.e ~ 1 + (1 | .cluster),
             data    = data.frame(.e = e_hat, .cluster = cluster_id,
                                  .w = weights),
             weights = .w,
             REML    = FALSE,
             control = lmerControl(optimizer = "bobyqa",
                                   optCtrl   = list(maxfun = 1e5)))
      ),
      error = function(e) {
        cat("    [LMM error iter", iter, "]:", conditionMessage(e), "\n")
        NULL
      }
    )
    if (is.null(lmm_model)) break

    re_vals <- ranef(lmm_model)[[".cluster"]]
    b_hat[] <- 0
    matched <- intersect(rownames(re_vals), names(b_hat))
    b_hat[matched] <- re_vals[matched, "(Intercept)"]

    ll_curr   <- as.numeric(logLik(lmm_model))
    delta_ll  <- abs(ll_curr - ll_prev)
    vc        <- as.data.frame(VarCorr(lmm_model))
    re_var    <- vc$vcov[vc$grp == ".cluster"]
    resid_var <- vc$vcov[vc$grp == "Residual"]

    iter_log <- rbind(iter_log,
                      data.frame(iter        = iter,
                                 rf_oob_rmse = sqrt(rf_model$prediction.error),
                                 re_var      = re_var,
                                 resid_var   = resid_var,
                                 log_lik     = ll_curr,
                                 delta_ll    = delta_ll))

    cat("  | OOB RMSE:", round(sqrt(rf_model$prediction.error), 5),
        "| RE var:",     round(re_var,    6),
        "| deltaLogLik:", round(delta_ll, 6), "\n")

    re_var_prev   <- if (iter > 1) iter_log$re_var[iter - 1] else NA
    re_var_stable <- !is.na(re_var_prev) && abs(re_var - re_var_prev) < 1e-6

    if (iter > 1 && (delta_ll < tol || re_var_stable)) {
      cat("  Converged at iteration", iter,
          if (re_var_stable) "(RE variance stable)" else "(deltaLogLik < tol)",
          "\n")
      converged <- TRUE
      break
    }
    ll_prev <- ll_curr
  }

  if (!converged) cat("  Did not converge within", max_iter, "iterations.\n")

  imp_df <- data.frame(
    variable   = names(rf_model$variable.importance),
    importance = as.numeric(rf_model$variable.importance)
  )
  imp_df <- imp_df[order(imp_df$importance, decreasing = TRUE), ]
  imp_df$pct <- imp_df$importance / sum(imp_df$importance) * 100
  rownames(imp_df) <- NULL

  cat("\n  Variable Importance:\n")
  print(imp_df)

  b_vec_final              <- b_hat[as.character(cluster_id)]
  b_vec_final[is.na(b_vec_final)] <- 0
  rmse_final <- sqrt(mean((y - (rf_model$predictions + b_vec_final))^2,
                          na.rm = TRUE))
  cat("\n  Final combined RMSE (train):", round(rmse_final, 5), "\n")

  list(rf_model   = rf_model,  lmm_model  = lmm_model,
       b_hat      = b_hat,     importance = imp_df,
       iter_log   = iter_log,  converged  = converged,
       rmse_final = rmse_final, n_iter    = nrow(iter_log))
}
```
```{r gmerf-fit}
cat("\n", rep("=", 55), "\n", sep = "")
cat("FITTING GMERF ON FULL TRAINING DATA\n")
cat(rep("=", 55), "\n\n", sep = "")

gmerf_models <- list(
  Politicians = fit_gmerf(df_train$Politicians, "Politicians"),
  Newspeople  = fit_gmerf(df_train$Newspeople,  "Newspeople"),
  Activists   = fit_gmerf(df_train$Activists,   "Activists")
)

save(gmerf_models, file = paste0(rdataPath, "gmerf_models.RData"))
cat("\nGMERF models saved.\n")

cat("\n===== GMERF Summary =====\n")
iwalk(gmerf_models, function(m, nm) {
  if (is.null(m)) return()
  vc <- as.data.frame(VarCorr(m$lmm_model))
  cat("\n--", nm, "--\n")
  cat("  Converged  :", m$converged, "| Iterations:", m$n_iter, "\n")
  cat("  Train RMSE :", round(m$rmse_final, 5), "\n")
  cat("  RE variance:", round(vc$vcov[vc$grp == ".cluster"], 6), "\n")
  cat("  Resid var  :", round(vc$vcov[vc$grp == "Residual"],  6), "\n")
  cat("  Top predictors:\n")
  print(head(m$importance, 5))
})
```

## GMERF Cross-Validation
```{r gmerf-cv-function}
evaluate_gmerf_cv <- function(data,
                               dataset_name,
                               n_folds    = 5,
                               predictors = c("MediaAttached", "TextComplexity",
                                              "MoralWords", "MoralEmotionalWords",
                                              "EmotionalWords", "WordCount", "Quote"),
                               seed = 123) {

  cat("\nCV Evaluation:", dataset_name, "\n")
  set.seed(seed)

  df <- data
  for (p in predictors) {
    if (p %in% names(df) && is.logical(df[[p]])) df[[p]] <- as.numeric(df[[p]])
  }
  df[[".cluster"]] <- factor(df[["UserID"]])
  df[[".y"]]       <- df[["ProportionOfHate"]]
  df[[".weight"]]  <- df[["Replies"]] / mean(df[["Replies"]])
  df <- df[complete.cases(df[, c(".y", ".weight", ".cluster", predictors)]), ]

  user_ids <- levels(df$.cluster)
  fold_map <- setNames(
    sample(rep(seq_len(n_folds), length.out = length(user_ids))),
    user_ids
  )
  df$fold <- fold_map[as.character(df$.cluster)]

  rf_formula   <- as.formula(paste(".y_star ~",
                                   paste(predictors, collapse = " + ")))
  fold_metrics <- data.frame(fold = integer(0), rmse = numeric(0),
                              mae  = numeric(0), r2   = numeric(0))

  for (k in seq_len(n_folds)) {
    train <- df[df$fold != k, ]
    test  <- df[df$fold == k, ]

    b_hat_cv       <- setNames(rep(0, length(levels(train$.cluster))),
                               levels(train$.cluster))
    rf_cv          <- NULL
    re_var_prev_cv <- NA

    for (iter in seq_len(15)) {
      b_vec              <- b_hat_cv[as.character(train$.cluster)]
      b_vec[is.na(b_vec)] <- 0
      rf_df_cv           <- train[, predictors, drop = FALSE]
      rf_df_cv[[".y_star"]] <- train$.y - b_vec

      rf_cv <- ranger(
        formula      = rf_formula,
        data         = rf_df_cv,
        num.trees    = 300,
        importance   = "none",
        case.weights = train$.weight,
        seed         = seed,
        num.threads  = parallel::detectCores() - 1
      )

      f_hat_cv <- predict(rf_cv, data = rf_df_cv)$predictions
      e_hat_cv <- train$.y - f_hat_cv

      lmm_cv <- tryCatch(
        suppressWarnings(
          lmer(.e ~ 1 + (1 | .cluster),
               data    = data.frame(.e       = e_hat_cv,
                                    .cluster = train$.cluster,
                                    .w       = train$.weight),
               weights = .w,
               REML    = FALSE,
               control = lmerControl(optimizer = "bobyqa",
                                     optCtrl   = list(maxfun = 1e5)))
        ),
        error = function(e) NULL
      )
      if (is.null(lmm_cv)) break

      re_vals <- ranef(lmm_cv)[[".cluster"]]
      b_hat_cv[] <- 0
      matched    <- intersect(rownames(re_vals), names(b_hat_cv))
      b_hat_cv[matched] <- re_vals[matched, "(Intercept)"]

      re_var_now <- as.data.frame(VarCorr(lmm_cv))$vcov[1]
      if (iter > 1 && abs(re_var_now - re_var_prev_cv) < 1e-6) break
      re_var_prev_cv <- re_var_now
    }

    test_pred <- pmax(0, pmin(1,
      predict(rf_cv, data = test[, predictors, drop = FALSE])$predictions +
      replace(b_hat_cv[as.character(test$.cluster)],
              is.na(b_hat_cv[as.character(test$.cluster)]), 0)
    ))

    actual <- test$.y
    ss_res <- sum((actual - test_pred)^2,         na.rm = TRUE)
    ss_tot <- sum((actual - mean(actual))^2,       na.rm = TRUE)
    rmse_k <- sqrt(mean((actual - test_pred)^2,   na.rm = TRUE))
    mae_k  <- mean(abs(actual - test_pred),        na.rm = TRUE)
    r2_k   <- 1 - ss_res / ss_tot

    cat("  Fold", k, "| n =", nrow(test),
        "| RMSE:", round(rmse_k, 5),
        "| MAE:",  round(mae_k,  5),
        "| R2:",   round(r2_k,   4), "\n")

    fold_metrics <- rbind(fold_metrics,
                          data.frame(fold = k, rmse = rmse_k,
                                     mae  = mae_k, r2 = r2_k))
  }

  cat("  Mean RMSE:", round(mean(fold_metrics$rmse), 5),
      "(SD:", round(sd(fold_metrics$rmse), 5), ")\n")
  cat("  Mean MAE :", round(mean(fold_metrics$mae),  5),
      "(SD:", round(sd(fold_metrics$mae),  5), ")\n")
  cat("  Mean R2  :", round(mean(fold_metrics$r2),   4),
      "(SD:", round(sd(fold_metrics$r2),   4), ")\n")

  list(fold_metrics = fold_metrics,
       mean_rmse    = mean(fold_metrics$rmse),
       mean_mae     = mean(fold_metrics$mae),
       mean_r2      = mean(fold_metrics$r2))
}
```
```{r gmerf-cv-run}
cat("\n", rep("=", 55), "\n", sep = "")
cat("GMERF CROSS-VALIDATION\n")
cat(rep("=", 55), "\n\n", sep = "")

cv_results <- list(
  Politicians = evaluate_gmerf_cv(df_train$Politicians, "Politicians"),
  Newspeople  = evaluate_gmerf_cv(df_train$Newspeople,  "Newspeople"),
  Activists   = evaluate_gmerf_cv(df_train$Activists,   "Activists")
)

save(cv_results, file = paste0(rdataPath, "gmerf_cv_results.RData"))
cat("\nGMERF CV results saved.\n")
```

# Model Comparison
```{r model-comparison}
if (!exists("bb_cv_results"))
  load(paste0(rdataPath, "bb_cv_results.RData"))
if (!exists("gamm_cv_results"))
  load(paste0(rdataPath, "gamm_cv_results.RData"))
if (!exists("cv_results"))
  load(paste0(rdataPath, "gmerf_cv_results.RData"))

cat("\n", rep("=", 50), "\n", sep = "")
cat("COMPLETE MODEL COMPARISON WITH CV\n")
cat(rep("=", 50), "\n", sep = "")

comparison_df_full <- data.frame(
  Dataset    = character(), Model      = character(),
  AIC        = numeric(),   LogLik     = numeric(),
  Train_RMSE = numeric(),   CV_RMSE    = numeric(),
  Train_R2   = numeric(),   CV_R2      = numeric(),
  stringsAsFactors = FALSE
)

for (nm in names(bb_models)) {
  m <- bb_models[[nm]]
  if (is.null(m)) next
  pred   <- predict(m, type = "response")
  actual <- with(df_train[[nm]], HReplies / Replies)
  comparison_df_full <- rbind(comparison_df_full, data.frame(
    Dataset    = nm, Model      = "BB",
    AIC        = tryCatch(AIC(m), error = function(e) NA),
    LogLik     = tryCatch(as.numeric(logLik(m)), error = function(e) NA),
    Train_RMSE = sqrt(mean((actual - pred)^2, na.rm = TRUE)),
    CV_RMSE    = bb_cv_results[[nm]]$mean_rmse,
    Train_R2   = cor(actual, pred, use = "complete.obs")^2,
    CV_R2      = bb_cv_results[[nm]]$mean_r2,
    stringsAsFactors = FALSE
  ))
}

for (nm in names(gamm_models)) {
  m <- gamm_models[[nm]]
  if (is.null(m)) next
  pred   <- predict(m, type = "response")
  actual <- with(df_train[[nm]], HReplies / Replies)
  comparison_df_full <- rbind(comparison_df_full, data.frame(
    Dataset    = nm, Model      = "GAMM",
    AIC        = AIC(m),
    LogLik     = as.numeric(logLik(m)),
    Train_RMSE = sqrt(mean((actual - pred)^2, na.rm = TRUE)),
    CV_RMSE    = gamm_cv_results[[nm]]$mean_rmse,
    Train_R2   = cor(actual, pred, use = "complete.obs")^2,
    CV_R2      = gamm_cv_results[[nm]]$mean_r2,
    stringsAsFactors = FALSE
  ))
}

for (nm in names(gmerf_models)) {
  m <- gmerf_models[[nm]]
  if (is.null(m)) next
  comparison_df_full <- rbind(comparison_df_full, data.frame(
    Dataset    = nm, Model      = "GMERF",
    AIC        = NA,
    LogLik     = as.numeric(logLik(m$lmm_model)),
    Train_RMSE = m$rmse_final,
    CV_RMSE    = cv_results[[nm]]$mean_rmse,
    Train_R2   = NA,
    CV_R2      = cv_results[[nm]]$mean_r2,
    stringsAsFactors = FALSE
  ))
}

comparison_df_full <- comparison_df_full[
  order(comparison_df_full$Dataset, comparison_df_full$Model), ]
comparison_df_full$Best_CV_RMSE <- ""
comparison_df_full$Best_CV_R2   <- ""

for (ds in unique(comparison_df_full$Dataset)) {
  idx <- comparison_df_full$Dataset == ds
  cv_vals <- comparison_df_full$CV_RMSE[idx]
  r2_vals <- comparison_df_full$CV_R2[idx]
  if (any(!is.na(cv_vals)))
    comparison_df_full$Best_CV_RMSE[idx][which.min(cv_vals)] <- "***"
  if (any(!is.na(r2_vals)))
    comparison_df_full$Best_CV_R2[idx][which.max(r2_vals)]   <- "***"
}

cat("\nNote: AIC not comparable across model families (BB vs GAMM).\n")
cat("Primary comparison metric is CV_RMSE (out-of-sample).\n\n")
print(comparison_df_full[, c("Dataset", "Model", "AIC", "Train_RMSE",
                              "CV_RMSE", "Train_R2", "CV_R2",
                              "Best_CV_RMSE", "Best_CV_R2")],
      row.names = FALSE, digits = 5)

cat("\n", rep("=", 50), "\n", sep = "")
```

# Test Set Evaluation
```{r test-set}
if (!exists("bb_models"))    load(paste0(rdataPath, "bb_models.RData"))
if (!exists("gamm_models"))  load(paste0(rdataPath, "gamm_models.RData"))
if (!exists("gmerf_models")) load(paste0(rdataPath, "gmerf_models.RData"))

cat("\n", rep("=", 50), "\n", sep = "")
cat("TEST SET EVALUATION\n")
cat(rep("=", 50), "\n", sep = "")

cat("Test set sizes:\n")
walk2(df_test, names(df_test), ~ cat(" ", .y, ":", nrow(.x), "rows\n"))

test_results <- data.frame(
  Dataset = character(), Model = character(),
  RMSE    = numeric(),   MAE   = numeric(),
  R2      = numeric(),   n     = integer(),
  stringsAsFactors = FALSE
)

predictors <- c("MediaAttached", "TextComplexity", "MoralWords",
                "MoralEmotionalWords", "EmotionalWords", "WordCount", "Quote")

for (nm in names(df_test)) {

  cat("\n", rep("-", 45), "\n", sep = "")
  cat("Dataset:", nm, "\n")

  # Keep original variable types to match what BB and GAMM were trained on
  test_df <- df_test[[nm]] %>%
    mutate(
      UserID = factor(UserID),
      .prop  = HReplies / Replies
    ) %>%
    filter(!is.na(.prop), Replies > 0)

  actual <- test_df$.prop
  n_test <- nrow(test_df)

  eval_preds <- function(pred, model_name, dataset_name) {
    pred   <- pmax(0, pmin(1, pred))
    ss_res <- sum((actual - pred)^2,         na.rm = TRUE)
    ss_tot <- sum((actual - mean(actual))^2, na.rm = TRUE)
    rmse   <- sqrt(mean((actual - pred)^2,   na.rm = TRUE))
    mae    <- mean(abs(actual - pred),        na.rm = TRUE)
    r2     <- 1 - ss_res / ss_tot

    cat(" ", model_name,
        "| RMSE:", round(rmse, 5),
        "| MAE:",  round(mae,  5),
        "| R2:",   round(r2,   4), "\n")

    data.frame(Dataset = dataset_name, Model = model_name,
               RMSE = rmse, MAE = mae, R2 = r2, n = n_test,
               stringsAsFactors = FALSE)
  }

  # ── BB ───────────────────────────────────────────────────────────────────────
  if (!is.null(bb_models[[nm]])) {
    pred <- tryCatch(
      predict(bb_models[[nm]], newdata = test_df, type = "response",
              allow.new.levels = TRUE),
      error = function(e) { cat("  BB predict error:", e$message, "\n"); NULL }
    )
    if (!is.null(pred))
      test_results <- rbind(test_results, eval_preds(pred, "BB", nm))
  }

  # ── GAMM ─────────────────────────────────────────────────────────────────────
  if (!is.null(gamm_models[[nm]])) {
    pred <- tryCatch(
      predict(gamm_models[[nm]], newdata = test_df, type = "response",
              exclude = "s(UserID)"),
      error = function(e) { cat("  GAMM predict error:", e$message, "\n"); NULL }
    )
    if (!is.null(pred))
      test_results <- rbind(test_results, eval_preds(pred, "GAMM", nm))
  }

  # ── GMERF ────────────────────────────────────────────────────────────────────
  if (!is.null(gmerf_models[[nm]])) {
    m <- gmerf_models[[nm]]

    # GMERF needs numeric predictors - coerce here only for GMERF
    test_pred_df <- test_df %>%
      mutate(MediaAttached = as.numeric(MediaAttached),
             Quote         = as.numeric(Quote))
    test_pred_df <- test_pred_df[, predictors, drop = FALSE]

    rf_pred <- tryCatch(
      predict(m$rf_model, data = test_pred_df)$predictions,
      error = function(e) { cat("  GMERF predict error:", e$message, "\n"); NULL }
    )

    if (!is.null(rf_pred)) {
      test_re      <- m$b_hat[as.character(test_df$UserID)]
      test_re[is.na(test_re)] <- 0
      pred         <- rf_pred + test_re
      test_results <- rbind(test_results, eval_preds(pred, "GMERF", nm))
    }
  }
}

test_results <- test_results[order(test_results$Dataset, test_results$Model), ]
test_results$Best_RMSE <- ""
test_results$Best_R2   <- ""

for (ds in unique(test_results$Dataset)) {
  idx <- test_results$Dataset == ds
  test_results$Best_RMSE[idx][which.min(test_results$RMSE[idx])] <- "***"
  test_results$Best_R2[idx][which.max(test_results$R2[idx])]     <- "***"
}

cat("\n", rep("=", 50), "\n", sep = "")
cat("FINAL TEST SET RESULTS\n")
cat(rep("=", 50), "\n\n", sep = "")
print(test_results[, c("Dataset", "Model", "n", "RMSE", "MAE",
                        "R2", "Best_RMSE", "Best_R2")],
      row.names = FALSE, digits = 5)

cat("\n", rep("-", 45), "\n", sep = "")
cat("Test RMSE vs CV RMSE (overfitting check):\n\n")

for (nm in unique(test_results$Dataset)) {
  cat(nm, ":\n")
  for (mod in c("BB", "GAMM", "GMERF")) {
    test_rmse <- test_results$RMSE[
      test_results$Dataset == nm & test_results$Model == mod
    ]
    cv_rmse <- switch(mod,
      BB    = if (exists("bb_cv_results"))
                bb_cv_results[[nm]]$mean_rmse   else NA,
      GAMM  = if (exists("gamm_cv_results"))
                gamm_cv_results[[nm]]$mean_rmse else NA,
      GMERF = if (exists("cv_results") && nm %in% names(cv_results))
                cv_results[[nm]]$mean_rmse      else NA
    )
    if (length(test_rmse) > 0 && !is.na(cv_rmse)) {
      cat("  ", mod,
          "| Test RMSE:", round(test_rmse, 5),
          "| CV RMSE:",   round(cv_rmse,   5),
          "| Diff:",      round(test_rmse - cv_rmse, 5), "\n")
    }
  }
}

save(test_results, file = paste0(rdataPath, "test_results.RData"))
cat("\nTest results saved.\n")
cat(rep("=", 50), "\n", sep = "")
```

# Beta-Binomial 99% Confidence Intervals
```{r}
bb_99ci <- imap(bb_models, function(m, nm) {
  tryCatch(
    confint(m, level = 0.99, method = "Wald"),
    error = function(e) { cat("CI error:", nm, e$message, "\n"); NULL }
  )
})
save(bb_99ci, file = paste0(rdataPath, "bb_99ci.RData"))

cat("BB MODEL: COEFFICIENTS AND 99% CONFIDENCE INTERVALS\n\n")

var_labels <- c(
  "(Intercept)"         = "Intercept",
  "MediaAttachedTRUE"   = "Media Attached",
  "TextComplexity"      = "Text Complexity",
  "MoralWords"          = "Moral Words",
  "MoralEmotionalWords" = "Moral-Emotional Words",
  "EmotionalWords"      = "Emotional Words",
  "WordCount"           = "Word Count",
  "QuoteTRUE"           = "Quote"
)

for (nm in names(bb_99ci)) {
  ci  <- bb_99ci[[nm]]
  cat("--", nm, "--\n")
  cat(sprintf("%-25s %8s %8s %8s %10s %10s\n",
              "Variable", "Coef", "OR", "OR%", "99% CI low", "99% CI high"))
  cat(rep("-", 73), "\n")
  
  for (v in names(var_labels)) {
    if (v %in% rownames(ci)) {
      coef_val <- ci[v, "Estimate"]
      lo       <- ci[v, 1]
      hi       <- ci[v, 2]
      or_val   <- exp(coef_val)
      or_pct   <- (or_val - 1) * 100
      or_lo    <- exp(lo)
      or_hi    <- exp(hi)
      cat(sprintf("%-25s %8.4f %8.4f %7.2f%% %10.4f %10.4f\n",
                  var_labels[v], coef_val, or_val, or_pct, or_lo, or_hi))
    }
  }
  cat("\n")
}

```

# GAMM Parametric Coefficient Table
```{r}
gamm_parametric <- imap(gamm_models, function(m, nm) {
  summary(m)$p.table
})
save(gamm_parametric, file = paste0(rdataPath, "gamm_parametric.RData"))

cat("GAMM MODEL: PARAMETRIC COEFFICIENTS\n\n")

for (nm in names(gamm_parametric)) {
  pt <- gamm_parametric[[nm]]
  cat("--", nm, "--\n")
  cat(sprintf("%-20s %10s %10s %10s %12s\n",
              "Variable", "Estimate", "Std.Error", "z value", "p value"))
  cat(rep("-", 65), "\n")
  
  for (v in rownames(pt)) {
    label <- ifelse(v %in% names(var_labels), var_labels[v], v)
    pval  <- pt[v, 4]
    pval_fmt <- ifelse(pval < 0.001, "<0.001", round(pval, 4))
    cat(sprintf("%-20s %10.4f %10.4f %10.4f %12s\n",
                label,
                pt[v, 1],
                pt[v, 2],
                pt[v, 3],
                pval_fmt))
  }
  cat("\n")
}
```

# Generate Visualizations

## Coefficient Comparison Plot
```{r}
# Build coefficient dataframe from BB models
coef_plot_data <- imap_dfr(bb_models, function(m, nm) {
  ci  <- bb_99ci[[nm]]
  vars_to_plot <- c("MoralWords", "MoralEmotionalWords",
                    "EmotionalWords", "WordCount", "TextComplexity")
  var_labels <- c(
    "MoralWords"          = "Moral Words",
    "MoralEmotionalWords" = "Moral-Emotional Words",
    "EmotionalWords"      = "Emotional Words",
    "WordCount"           = "Word Count",
    "TextComplexity"      = "Text Complexity"
  )
  
  data.frame(
    dataset  = nm,
    variable = var_labels[vars_to_plot],
    estimate = ci[vars_to_plot, "Estimate"],
    ci_low   = ci[vars_to_plot, 1],
    ci_high  = ci[vars_to_plot, 2],
    stringsAsFactors = FALSE
  )
}) %>%
  mutate(
    dataset  = factor(dataset,  levels = c("Politicians", "Newspeople", "Activists")),
    variable = factor(variable, levels = rev(c("Moral Words", "Moral-Emotional Words",
                                               "Emotional Words", "Word Count",
                                               "Text Complexity")))
  )

colors <- wes_palette("Darjeeling1")[c(1, 2, 3)]

p_coef <- ggplot(coef_plot_data,
                 aes(x = variable, y = estimate,
                     ymin = ci_low, ymax = ci_high,
                     color = dataset, group = dataset)) +
  geom_hline(yintercept = 0, color = "grey50", linetype = "dashed") +
  geom_pointrange(position = position_dodge(width = 0.5),
                  linewidth = 0.6, size = 0.8) +
  coord_flip() +
  scale_color_manual(values = colors) +
  scale_y_continuous(breaks = seq(-0.02, 0.20, by = 0.02)) +
  labs(
    title   = "Effect of Moralized Language on Hate Speech (Betabinomial Model)",
    subtitle = "Coefficient estimates with 99% confidence intervals",
    x       = NULL,
    y       = "Coefficient Estimate",
    color   = NULL
  ) +
  theme_bw() +
  theme(
    legend.position   = c(0.82, 0.2),
    legend.background = element_rect(fill = "white", color = "grey80"),
    axis.text.y       = element_text(size = 11),
    axis.text.x       = element_text(size = 10),
    plot.title        = element_text(size = 13, face = "bold"),
    plot.subtitle     = element_text(size = 10, color = "grey40")
  )

print(p_coef)
ggsave(paste0(graphPath, "BB_coefficient_plot.pdf"),
       p_coef, width = 18, height = 10, units = "cm", scale = 1.2)
```

## Model Comparison CV RMSE Bar Chart
```{r}
cv_compare_data <- bind_rows(
  imap_dfr(bb_cv_results, function(x, nm) {
    data.frame(Dataset = nm, Model = "BB",
               CV_RMSE = x$mean_rmse,
               SD      = sd(x$fold_metrics$rmse),
               stringsAsFactors = FALSE)
  }),
  imap_dfr(gamm_cv_results, function(x, nm) {
    data.frame(Dataset = nm, Model = "GAMM",
               CV_RMSE = x$mean_rmse,
               SD      = sd(x$fold_metrics$rmse),
               stringsAsFactors = FALSE)
  }),
  imap_dfr(gmerf_cv_results, function(x, nm) {
    data.frame(Dataset = nm, Model = "GMERF",
               CV_RMSE = x$mean_rmse,
               SD      = sd(x$fold_metrics$rmse),
               stringsAsFactors = FALSE)
  })
) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Model   = factor(Model,   levels = c("BB", "GAMM", "GMERF"))
  )

p_cv <- ggplot(cv_compare_data,
               aes(x = Dataset, y = CV_RMSE, fill = Model)) +
  geom_col(position = position_dodge(width = 0.7),
           width = 0.6, color = "white") +
  geom_errorbar(aes(ymin = CV_RMSE - SD, ymax = CV_RMSE + SD),
                position = position_dodge(width = 0.7),
                width = 0.2, color = "grey30") +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(1, 2, 3)]) +
  scale_y_continuous(limits = c(0, 0.12),
                     breaks = seq(0, 0.12, by = 0.02)) +
  labs(
    title    = "Cross-Validation RMSE by Model and Dataset",
    subtitle = "Error bars show standard deviation across 5 folds",
    x        = NULL,
    y        = "Mean CV RMSE",
    fill     = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 11),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_cv)
ggsave(paste0(graphPath, "CV_RMSE_comparison.pdf"),
       p_cv, width = 18, height = 10, units = "cm", scale = 1.2)
```

## GAMM Smooth Plots for MoralWords

```{r}
library(mgcv)

smooth_data <- imap_dfr(gamm_models, function(m, nm) {
  
  # Generate prediction grid for MoralWords
  moral_range <- range(m$model[["MoralWords"]], na.rm = TRUE)
  newdata <- data.frame(
    MoralWords          = seq(moral_range[1], moral_range[2], length.out = 200),
    MoralEmotionalWords = 0,
    EmotionalWords      = 0,
    WordCount           = median(m$model[["WordCount"]], na.rm = TRUE),
    TextComplexity      = median(m$model[["TextComplexity"]], na.rm = TRUE),
    MediaAttached       = FALSE,
    Quote               = FALSE,
    UserID              = m$model[["UserID"]][1]
  )
  
  pred <- predict(m, newdata = newdata, type = "link",
                  se.fit = TRUE, exclude = "s(UserID)")
  
  data.frame(
    Dataset      = nm,
    MoralWords   = newdata$MoralWords,
    fit          = pred$fit,
    se           = pred$se.fit,
    fit_lo       = pred$fit - 2 * pred$se.fit,
    fit_hi       = pred$fit + 2 * pred$se.fit,
    stringsAsFactors = FALSE
  )
}) %>%
  mutate(Dataset = factor(Dataset,
                          levels = c("Politicians", "Newspeople", "Activists")))

p_smooth <- ggplot(smooth_data,
                   aes(x = MoralWords, y = fit)) +
  geom_ribbon(aes(ymin = fit_lo, ymax = fit_hi),
              fill = "steelblue", alpha = 0.2) +
  geom_line(color = "steelblue", linewidth = 1) +
  facet_wrap(~ Dataset, scales = "free_x") +
  labs(
    title    = "Non-Linear Effect of Moral Words on Hate Speech (GAMM)",
    subtitle = "Predicted log-odds with 95% confidence band; other predictors held at median",
    x        = "Moral Word Count",
    y        = "Predicted Log-Odds of Hate Speech"
  ) +
  theme_bw() +
  theme(
    strip.text    = element_text(size = 11, face = "bold"),
    axis.text     = element_text(size = 9),
    plot.title    = element_text(size = 13, face = "bold"),
    plot.subtitle = element_text(size = 10, color = "grey40")
  )

print(p_smooth)
ggsave(paste0(graphPath, "GAMM_MoralWords_smooth.pdf"),
       p_smooth, width = 22, height = 9, units = "cm", scale = 1.2)

```

## GMERF Variable Importance Chart

```{r}
importance_data <- imap_dfr(gmerf_models, function(m, nm) {
  m$importance %>%
    mutate(Dataset = nm)
}) %>%
  mutate(
    Dataset  = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    variable = case_match(variable,
      "TextComplexity"      ~ "Text Complexity",
      "WordCount"           ~ "Word Count",
      "MoralWords"          ~ "Moral Words",
      "MoralEmotionalWords" ~ "Moral-Emotional Words",
      "EmotionalWords"      ~ "Emotional Words",
      "MediaAttached"       ~ "Media Attached",
      "Quote"               ~ "Quote",
      .default = variable
    ),
    variable = reorder(variable, pct)
  )

p_imp <- ggplot(importance_data,
                aes(x = variable, y = pct, fill = Dataset)) +
  geom_col(position = position_dodge(width = 0.7),
           width = 0.6, color = "white") +
  coord_flip() +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(1, 2, 3)]) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(
    title    = "GMERF Variable Importance by Dataset",
    subtitle = "Percentage of total impurity reduction attributed to each predictor",
    x        = NULL,
    y        = "Importance (%)",
    fill     = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 11),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_imp)
ggsave(paste0(graphPath, "GMERF_variable_importance.pdf"),
       p_imp, width = 18, height = 10, units = "cm", scale = 1.2)
```

## Robustness Check Coefficient Stability Plot

```{r}
robustness_sources <- list()

robustness_sources$main <- imap_dfr(bb_models, function(m, nm) {
  data.frame(Dataset = nm, Check = "Main model (BB)",
             Estimate = fixef(m)$cond["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_sources$source_hate <- imap_dfr(source_hate_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  data.frame(Dataset = nm, Check = "Source hate control",
             Estimate = fixef(m)["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_sources$binary <- imap_dfr(binary_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  coefs <- fixef(m)
  val   <- if ("MoralBinaryTRUE" %in% names(coefs)) coefs["MoralBinaryTRUE"] else NA
  data.frame(Dataset = nm, Check = "Binary indicator",
             Estimate = val, stringsAsFactors = FALSE)
})

robustness_sources$proportions <- imap_dfr(proportions_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  coefs <- fixef(m)
  val   <- if ("MoralWordsProp" %in% names(coefs)) coefs["MoralWordsProp"] else NA
  data.frame(Dataset = nm, Check = "Word proportions",
             Estimate = val, stringsAsFactors = FALSE)
})

if (exists("directed_results")) {
  robustness_sources$directed <- imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$directed)) return(NULL)
    data.frame(Dataset = nm, Check = "Directed hate",
               Estimate = fixef(x$directed)["MoralWords"],
               stringsAsFactors = FALSE)
  })
  robustness_sources$generalised <- imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$generalised)) return(NULL)
    data.frame(Dataset = nm, Check = "Generalised hate",
               Estimate = fixef(x$generalised)["MoralWords"],
               stringsAsFactors = FALSE)
  })
} else {
  cat("Note: directed_results not found - skipping directed/generalised hate checks.\n")
}

robustness_sources$interactions <- imap_dfr(interaction_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  data.frame(Dataset = nm, Check = "With interactions",
             Estimate = fixef(m)["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_data <- bind_rows(robustness_sources) %>%
  filter(!is.na(Estimate)) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Check   = factor(Check,   levels = unique(Check))
  )


robustness_data <- bind_rows(
  # Main model coefficients from BB
  imap_dfr(bb_models, function(m, nm) {
    data.frame(
      Dataset = nm, Check = "Main model (BB)",
      Estimate = fixef(m)$cond["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Source hate control
  imap_dfr(source_hate_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Source hate control",
      Estimate = fixef(m)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Binary indicator
  imap_dfr(binary_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    coefs <- fixef(m)
    val   <- if ("MoralBinaryTRUE" %in% names(coefs)) coefs["MoralBinaryTRUE"] else NA
    data.frame(
      Dataset = nm, Check = "Binary indicator",
      Estimate = val,
      stringsAsFactors = FALSE
    )
  }),
  # Proportions
  imap_dfr(proportions_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    coefs <- fixef(m)
    val   <- if ("MoralWordsProp" %in% names(coefs)) coefs["MoralWordsProp"] else NA
    data.frame(
      Dataset = nm, Check = "Word proportions",
      Estimate = val,
      stringsAsFactors = FALSE
    )
  }),
  # Directed hate
  imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$directed)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Directed hate",
      Estimate = fixef(x$directed)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Generalised hate
  imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$generalised)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Generalised hate",
      Estimate = fixef(x$generalised)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Interactions
  imap_dfr(interaction_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    data.frame(
      Dataset = nm, Check = "With interactions",
      Estimate = fixef(m)["MoralWords"],
      stringsAsFactors = FALSE
    )
  })
) %>%
  filter(!is.na(Estimate)) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Check   = factor(Check,   levels = c("Main model (BB)", "Source hate control",
                                          "Binary indicator", "Word proportions",
                                          "Directed hate", "Generalised hate",
                                          "With interactions"))
  )

p_robust <- ggplot(robustness_data,
                   aes(x = Check, y = Estimate, color = Dataset, group = Dataset)) +
  geom_hline(yintercept = 0, color = "grey50", linetype = "dashed") +
  geom_line(size = 0.8, alpha = 0.6) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = wes_palette("Darjeeling1")[c(1, 2, 3)]) +
  labs(
    title    = "MoralWords Coefficient Across Robustness Specifications",
    subtitle = "Positive values across all checks confirm robustness of the main finding",
    x        = NULL,
    y        = "MoralWords Coefficient Estimate",
    color    = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 10),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_robust)
ggsave(paste0(graphPath, "Robustness_MoralWords.pdf"),
       p_robust, width = 20, height = 10, units = "cm", scale = 1.2)
```

## Out-of-Sample R-Squared Improvement Table

```{r}
r2_improve_data <- bind_rows(
  imap_dfr(oos_r2_results, function(df, nm) {
    ratio <- df$Moral_vs_Content_ratio[
      df$Specification == "Author + Content + Moral"
    ]
    data.frame(Dataset = nm, Source = "Our replication",
               Ratio = ratio, stringsAsFactors = FALSE)
  }),
  data.frame(
    Dataset = c("Politicians", "Newspeople", "Activists"),
    Source  = "Parent paper",
    Ratio   = c(1.22, 1.55, 1.42),
    stringsAsFactors = FALSE
  )
) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Source  = factor(Source,  levels = c("Parent paper", "Our replication"))
  )

p_r2 <- ggplot(r2_improve_data,
               aes(x = Dataset, y = Ratio, fill = Source)) +
  geom_col(position = position_dodge(width = 0.6),
           width = 0.5, color = "white") +
  geom_hline(yintercept = 1, color = "grey40", linetype = "dashed") +
  scale_fill_manual(values = c("Parent paper"    = "grey60",
                               "Our replication" = "steelblue")) +
  scale_y_continuous(breaks = seq(0, 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
  labs(
    title    = "Out-of-Sample R² Improvement from Adding Moral Language",
    subtitle = "Ratio of moral language model R² to content-only model R²\nDashed line at 1.0 = no improvement",
    x        = NULL,
    y        = "R² Improvement Ratio",
    fill     = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 11),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_r2)
ggsave(paste0(graphPath, "OOS_R2_improvement.pdf"),
       p_r2, width = 16, height = 10, units = "cm", scale = 1.2)
```

```{r}
for (nm in unique(test_results$Dataset)) {
  cat(nm, ":\n")
  for (mod in c("BB", "GAMM", "GMERF")) {
    test_rmse <- test_results$RMSE[
      test_results$Dataset == nm & test_results$Model == mod
    ]
    cv_rmse <- switch(mod,
      BB    = if (exists("bb_cv_results"))
                bb_cv_results[[nm]]$mean_rmse   else NA,
      GAMM  = if (exists("gamm_cv_results"))
                gamm_cv_results[[nm]]$mean_rmse else NA,
      GMERF = if (exists("cv_results") && nm %in% names(cv_results))
                cv_results[[nm]]$mean_rmse      else NA
    )
    if (length(test_rmse) > 0 && !is.na(cv_rmse)) {
      cat("  ", mod,
          "| Test RMSE:", round(test_rmse, 5),
          "| CV RMSE:",   round(cv_rmse,   5),
          "| Diff:",      round(test_rmse - cv_rmse, 5), "\n")
    }
  }
}
```

