---
title: "Moralized Language Predicts Hate Speech (Supplements)"
author: KS
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{booktabs}
   - \usepackage{float}
   - \usepackage{longtable}
   - \usepackage{multirow}
   - \usepackage{siunitx}
output:
  pdf_document:
    toc: yes
    keep_tex: no
    number_sections: yes
---
```{r setup, include=FALSE}
library(tidyverse)
library(lme4)
library(glmmTMB)
library(mgcv)
library(ranger)
library(tidymodels)
library(broom)
library(broom.mixed)
library(car)
library(furrr)
library(wesanderson)

options(xtable.comment = FALSE, width = 80, scipen = 999)
plan(multisession, workers = parallel::detectCores() / 2)
source("utils.R")
```

```{r paths}
# Set this to wherever you cloned/downloaded the repository
# Example: "C:/Users/yourname/Downloads/DS340/"
# Example: "/Users/yourname/Documents/DS340/"
# Do NOT include a trailing slash
PROJECT_ROOT <- "C:/Users/Josh/OneDrive - The Pennsylvania State University/DS 340W"

# All other paths are derived automatically - do not change these
inputPath  <- paste0(PROJECT_ROOT, "/Data/")
splitPath  <- paste0(PROJECT_ROOT, "/Data/split_output/")
graphPath  <- paste0(PROJECT_ROOT, "/Data/Graphs/")
rdataPath  <- paste0(PROJECT_ROOT, "/R Data/")
```

```{r load-data}
load_dataset <- function(path, label) {
  read_csv(path, show_col_types = FALSE) %>%
    mutate(
      UserID     = factor(UserID),
      SourceHate = relevel(factor(SourceHate), "regular"),
      Dataset    = label
    )
}

df_train <- list(
  Politicians = load_dataset(paste0(splitPath, "df_politicians_train.csv"), "Politicians"),
  Newspeople  = load_dataset(paste0(splitPath, "df_newspeople_train.csv"),  "Newspeople"),
  Activists   = load_dataset(paste0(splitPath, "df_activists_train.csv"),   "Activists")
)

df_test <- list(
  Politicians = load_dataset(paste0(splitPath, "df_politicians_test.csv"), "Politicians"),
  Newspeople  = load_dataset(paste0(splitPath, "df_newspeople_test.csv"),  "Newspeople"),
  Activists   = load_dataset(paste0(splitPath, "df_activists_test.csv"),   "Activists")
)

cat("Training set sizes:\n")
walk2(df_train, names(df_train), ~ cat(" ", .y, ":", nrow(.x), "rows\n"))
cat("Test set sizes:\n")
walk2(df_test,  names(df_test),  ~ cat(" ", .y, ":", nrow(.x), "rows\n"))
```

```{r helper-functions}
# Standard GLMM formula used across all robustness checks
glmm_formula <- cbind(HReplies, Replies - HReplies) ~
  MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
  EmotionalWords + WordCount + Quote + (1 | UserID)

glmm_control <- glmerControl(
  optimizer = "bobyqa",
  optCtrl   = list(maxfun = 2e5)
)

# Fit a standard GLMM on any dataset
fit_glmm <- function(data, name, formula = glmm_formula) {
  cat("\nFitting GLMM:", name, "| n =", nrow(data),
      "| started:", format(Sys.time(), "%H:%M:%S"), "\n")
  start <- Sys.time()

  m <- suppressWarnings(
    tryCatch(
      glmer(formula, data = data, family = binomial(link = "logit"),
            control = glmm_control, nAGQ = 1),
      error = function(e) { cat("ERROR:", e$message, "\n"); NULL }
    )
  )

  cat("Completed in",
      round(difftime(Sys.time(), start, units = "mins"), 2), "mins\n")
  m
}

# Scale continuous predictors for models that need standardised inputs
scale_df <- function(df) {
  df %>% mutate(
    TextComplexityZ      = as.numeric(scale(TextComplexity)),
    MoralWordsZ          = as.numeric(scale(MoralWords)),
    MoralEmotionalWordsZ = as.numeric(scale(MoralEmotionalWords)),
    EmotionalWordsZ      = as.numeric(scale(EmotionalWords)),
    WordCountZ           = as.numeric(scale(WordCount)),
    RetweetCountZ        = as.numeric(scale(RetweetCount)),
    LikeCountZ           = as.numeric(scale(LikeCount))
  )
}

# Add word proportion variables
add_proportions <- function(df) {
  df %>% mutate(
    MoralWordsProp          = MoralWords / WordCount,
    MoralEmotionalWordsProp = MoralEmotionalWords / WordCount,
    EmotionalWordsProp      = EmotionalWords / WordCount
  )
}

# Add binary moral word indicators
add_binary <- function(df) {
  df %>% mutate(
    MoralBinary          = MoralWords > 0,
    MoralEmotionalBinary = MoralEmotionalWords > 0
  )
}

save.image()
```

# Out-of-Sample R² Comparison

Replicates the parent paper's key robustness claim: that adding moralized
language to a baseline content model improves out-of-sample R² by 1.22–1.55x.
Four model specifications are compared via 10-fold cross-validation.
```{r oos-r2-function}
evaluate_oos_r2 <- function(data, dataset_name, n_folds = 10, seed = 123) {

  cat("\nOut-of-sample R² evaluation:", dataset_name,
      "| n =", nrow(data), "\n")
  set.seed(seed)

  df <- data %>%
    mutate(
      MediaAttached = as.numeric(MediaAttached),
      Quote         = as.numeric(Quote)
    ) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  folds <- vfold_cv(df, v = n_folds)

  author_vars  <- c("Followers", "Followees", "AccountAge", "Verified")
  content_vars <- c("WordCount", "TextComplexity", "EmotionalWords",
                    "Quote", "MediaAttached")
  xyz_vars     <- c("XYZCount")
  moral_vars   <- c("MoralWords", "MoralEmotionalWords")

  specs <- list(
    "Author only"                  = author_vars,
    "Author + Content"             = c(author_vars, content_vars),
    "Author + Content + XYZ"       = c(author_vars, content_vars, xyz_vars),
    "Author + Content + Moral"     = c(author_vars, content_vars, moral_vars)
  )

  mod_glm <- linear_reg() %>%
    set_engine("lm") %>%
    translate()

  results <- imap(specs, function(vars, spec_name) {
    cat("  Fitting:", spec_name, "\n")
    wf <- workflow() %>%
      add_variables(outcomes    = "ProportionOfHate",
                    predictors  = all_of(vars)) %>%
      add_model(mod_glm,
                formula = as.formula(
                  paste("ProportionOfHate ~", paste(vars, collapse = " + "))
                ))
    tryCatch(
      fit_resamples(wf, folds, metrics = metric_set(rsq)) %>%
        collect_metrics() %>% pull(mean),
      error = function(e) { cat("  Error:", e$message, "\n"); NA }
    )
  })

  r2_df <- data.frame(
    Specification          = names(results),
    R2                     = unlist(results),
    stringsAsFactors       = FALSE
  )

  content_r2 <- r2_df$R2[r2_df$Specification == "Author + Content"]
  moral_r2   <- r2_df$R2[r2_df$Specification == "Author + Content + Moral"]
  r2_df$Moral_vs_Content_ratio <- NA
  r2_df$Moral_vs_Content_ratio[
    r2_df$Specification == "Author + Content + Moral"
  ] <- round(moral_r2 / content_r2, 3)

  cat("\nResults for", dataset_name, ":\n")
  print(r2_df, row.names = FALSE, digits = 4)
  cat("\nMoral language improvement over content model:",
      round(moral_r2 / content_r2, 3), "x\n")
  cat("Parent paper reported: 1.22x (Pol), 1.55x (News), 1.42x (Act)\n")

  r2_df
}
```

```{r oos-r2-run}
oos_r2_results <- list(
  Politicians = evaluate_oos_r2(df_train_sample$Politicians, "Politicians"),
  Newspeople  = evaluate_oos_r2(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = evaluate_oos_r2(df_train_sample$Activists,   "Activists")
)

save(oos_r2_results, file = "oos_r2_results.RData")
cat("\nOut-of-sample R² results saved.\n")
```

# XYZ Implausible Model Test

Sanity check from the parent paper: a model using counts of X, Y, and Z
letters as predictors should perform worse than the main model and show
near-zero coefficients.
```{r xyz-function}
run_xyz_implausible_test <- function(data, dataset_name) {

  cat("\nXYZ Implausible Model Test:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- data %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  # Main model
  main_model <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalWords + WordCount + Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  # Implausible model
  xyz_model <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + XYZCount +
        EmotionalWords + WordCount + Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("  Main model AIC:        ", round(AIC(main_model), 2), "\n")
  cat("  Implausible model AIC: ", round(AIC(xyz_model),  2), "\n")
  cat("  AIC difference (main - implausible):",
      round(AIC(main_model) - AIC(xyz_model), 2),
      "(negative = main model better)\n")
  cat("  XYZ coefficient:", round(fixef(xyz_model)["XYZCount"], 6),
      "(should be near zero)\n")

  list(main_model = main_model, xyz_model = xyz_model,
       aic_main   = AIC(main_model), aic_xyz = AIC(xyz_model),
       xyz_coef   = fixef(xyz_model)["XYZCount"])
}
```

```{r xyz-run}
xyz_results <- list(
  Politicians = run_xyz_implausible_test(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_xyz_implausible_test(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_xyz_implausible_test(df_train_sample$Activists,   "Activists")
)

save(xyz_results, file = "xyz_results.RData")
cat("\nXYZ implausible model results saved.\n")
```

# Source Hate Robustness Check

Tests whether the moral language effect persists after controlling for
whether the source tweet itself was hateful.
```{r source-hate-function}
run_source_hate_check <- function(data, dataset_name) {

  cat("\nSource Hate Robustness Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- data %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalWords + WordCount + Quote + SourceHate + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Coefficients:\n")
  print(round(summary(m)$coefficients, 4))
  cat("\n  MoralWords coef with SourceHate control:",
      round(fixef(m)["MoralWords"], 4), "\n")

  m
}
```

```{r source-hate-run}
source_hate_results <- list(
  Politicians = run_source_hate_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_source_hate_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_source_hate_check(df_train_sample$Activists,   "Activists")
)

save(source_hate_results, file = "source_hate_results.RData")
cat("\nSource hate robustness results saved.\n")
```

# Retweet Count Robustness Check

Tests whether the moral language effect persists after controlling for
social influence (retweet count). Uses standardised predictors.
```{r retweet-function}
run_retweet_check <- function(data, dataset_name) {

  cat("\nRetweet Robustness Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- scale_df(data) %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexityZ + MoralWordsZ +
        MoralEmotionalWordsZ + EmotionalWordsZ + WordCountZ +
        Quote + RetweetCountZ + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Coefficients:\n")
  print(round(summary(m)$coefficients, 4))
  cat("\n  MoralWordsZ coef with retweet control:",
      round(fixef(m)["MoralWordsZ"], 4), "\n")
  cat("  RetweetCountZ coef:",
      round(fixef(m)["RetweetCountZ"], 4), "\n")

  m
}
```

```{r retweet-run}
retweet_results <- list(
  Politicians = run_retweet_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_retweet_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_retweet_check(df_train_sample$Activists,   "Activists")
)

save(retweet_results, file = "retweet_results.RData")
cat("\nRetweet robustness results saved.\n")
```

# Like Count Robustness Check

Tests whether the moral language effect persists after controlling for
engagement (like count). Uses standardised predictors.
```{r likes-function}
run_likes_check <- function(data, dataset_name) {

  cat("\nLike Count Robustness Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- scale_df(data) %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexityZ + MoralWordsZ +
        MoralEmotionalWordsZ + EmotionalWordsZ + WordCountZ +
        Quote + LikeCountZ + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Coefficients:\n")
  print(round(summary(m)$coefficients, 4))
  cat("\n  MoralWordsZ coef with like count control:",
      round(fixef(m)["MoralWordsZ"], 4), "\n")
  cat("  LikeCountZ coef:",
      round(fixef(m)["LikeCountZ"], 4), "\n")

  m
}
```

```{r likes-run}
likes_results <- list(
  Politicians = run_likes_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_likes_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_likes_check(df_train_sample$Activists,   "Activists")
)

save(likes_results, file = "likes_results.RData")
cat("\nLike count robustness results saved.\n")
```

# Directed vs Generalised Hate Speech

Tests whether the moral language effect holds separately for directed
(second-person) and generalised (third-person) hate speech.
```{r directed-generalised-function}
run_directed_generalised <- function(data, dataset_name) {

  cat("\nDirected vs Generalised Hate Speech:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- data %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  # Directed hate (second-person)
  cat("  Fitting directed model...\n")
  m_directed <- suppressWarnings(
    glmer(
      cbind(HRepliesDirected, Replies - HRepliesDirected) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalWords + WordCount + Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  # Generalised hate (third-person)
  cat("  Fitting generalised model...\n")
  m_generalised <- suppressWarnings(
    glmer(
      cbind(HRepliesGeneralized, Replies - HRepliesGeneralized) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalWords + WordCount + Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Directed hate - MoralWords coef:",
      round(fixef(m_directed)["MoralWords"], 4), "\n")
  cat("  Generalised hate - MoralWords coef:",
      round(fixef(m_generalised)["MoralWords"], 4), "\n")

  list(directed = m_directed, generalised = m_generalised)
}
```
```{r directed-generalised-run}
directed_results <- list(
  Politicians = run_directed_generalised(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_directed_generalised(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_directed_generalised(df_train_sample$Activists,   "Activists")
)

save(directed_results, file = "directed_results.RData")
cat("\nDirected vs generalised hate speech results saved.\n")
```

# Word Proportions Robustness Check

Tests whether using word proportions (moral words / total words) instead
of raw counts changes the substantive conclusions.
```{r proportions-function}
run_proportions_check <- function(data, dataset_name) {

  cat("\nWord Proportions Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- add_proportions(data) %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralWordsProp +
        MoralEmotionalWordsProp + EmotionalWordsProp + WordCount +
        Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  MoralWordsProp coef:",
      round(fixef(m)["MoralWordsProp"], 4), "\n")
  cat("  MoralEmotionalWordsProp coef:",
      round(fixef(m)["MoralEmotionalWordsProp"], 4), "\n")

  m
}
```

```{r proportions-run}
proportions_results <- list(
  Politicians = run_proportions_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_proportions_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_proportions_check(df_train_sample$Activists,   "Activists")
)

save(proportions_results, file = "proportions_results.RData")
cat("\nProportions robustness results saved.\n")
```

# Binary Moral Words Robustness Check

Tests whether the effect holds when moral language is treated as a binary
presence/absence indicator rather than a count.
```{r binary-function}
run_binary_check <- function(data, dataset_name) {

  cat("\nBinary Moral Words Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- add_binary(data) %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralBinary +
        MoralEmotionalBinary + EmotionalWords + WordCount +
        Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  MoralBinary coef:",
      round(fixef(m)["MoralBinaryTRUE"], 4), "\n")
  cat("  MoralEmotionalBinary coef:",
      round(fixef(m)["MoralEmotionalBinaryTRUE"], 4), "\n")

  m
}
```

```{r binary-run}
binary_results <- list(
  Politicians = run_binary_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_binary_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_binary_check(df_train_sample$Activists,   "Activists")
)

save(binary_results, file = "binary_results.RData")
cat("\nBinary moral words results saved.\n")
```

# Positive and Negative Emotional Words

Tests whether separating emotional words into positive and negative
components changes the moral language effect estimates.
```{r distinct-emotions-function}
run_distinct_emotions <- function(data, dataset_name) {

  cat("\nDistinct Emotions Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- data %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalPositive + EmotionalNegative + WordCount +
        Quote + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Coefficients:\n")
  print(round(summary(m)$coefficients, 4))

  m
}
```

```{r distinct-emotions-run}
distinct_emotions_results <- list(
  Politicians = run_distinct_emotions(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_distinct_emotions(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_distinct_emotions(df_train_sample$Activists,   "Activists")
)

save(distinct_emotions_results, file = "distinct_emotions_results.RData")
cat("\nDistinct emotions results saved.\n")
```

# Interaction Effects

Tests whether moral words interact with word count — i.e., whether the
effect of moral language depends on tweet length.
```{r interactions-function}
run_interactions_check <- function(data, dataset_name) {

  cat("\nInteraction Effects Check:", dataset_name,
      "| n =", nrow(data), "\n")

  df <- data %>%
    mutate(MediaAttached = as.numeric(MediaAttached),
           Quote         = as.numeric(Quote)) %>%
    filter(!is.na(ProportionOfHate), Replies > 0)

  m <- suppressWarnings(
    glmer(
      cbind(HReplies, Replies - HReplies) ~
        MediaAttached + TextComplexity + MoralWords + MoralEmotionalWords +
        EmotionalWords + WordCount + Quote +
        MoralWords:WordCount + MoralEmotionalWords:WordCount + (1 | UserID),
      data    = df,
      family  = binomial(link = "logit"),
      control = glmm_control,
      nAGQ    = 1
    )
  )

  cat("\n  Coefficients:\n")
  print(round(summary(m)$coefficients, 4))
  cat("\n  MoralWords:WordCount interaction coef:",
      round(fixef(m)["MoralWords:WordCount"], 6), "\n")

  m
}
```

```{r interactions-run}
interaction_results <- list(
  Politicians = run_interactions_check(df_train_sample$Politicians, "Politicians"),
  Newspeople  = run_interactions_check(df_train_sample$Newspeople,  "Newspeople"),
  Activists   = run_interactions_check(df_train_sample$Activists,   "Activists")
)

save(interaction_results, file = "interaction_results.RData")
cat("\nInteraction effects results saved.\n")
```

# Robustness Summary
```{r robustness-summary}
cat("\n", rep("=", 55), "\n", sep = "")
cat("ROBUSTNESS SUMMARY\n")
cat(rep("=", 55), "\n\n", sep = "")

datasets <- c("Politicians", "Newspeople", "Activists")

# Main model MoralWords coefficients for reference
cat("Main model MoralWords coefficients (from XYZ check):\n")
for (nm in datasets) {
  m <- xyz_results[[nm]]$main_model
  if (!is.null(m))
    cat(" ", nm, ":", round(fixef(m)["MoralWords"], 4), "\n")
}

cat("\nMoralWords coefficients across robustness checks:\n\n")

checks <- list(
  "Source hate control" = lapply(source_hate_results,
    function(m) if (!is.null(m)) round(fixef(m)["MoralWords"], 4) else NA),
  "Retweet control" = lapply(retweet_results,
    function(m) if (!is.null(m)) round(fixef(m)["MoralWordsZ"], 4) else NA),
  "Like count control" = lapply(likes_results,
    function(m) if (!is.null(m)) round(fixef(m)["MoralWordsZ"], 4) else NA),
  "Word proportions" = lapply(proportions_results,
    function(m) if (!is.null(m)) round(fixef(m)["MoralWordsProp"], 4) else NA),
  "Binary indicator" = lapply(binary_results,
    function(m) if (!is.null(m)) round(fixef(m)["MoralBinaryTRUE"], 4) else NA),
  "Directed hate" = lapply(directed_results,
    function(x) if (!is.null(x$directed)) round(fixef(x$directed)["MoralWords"], 4) else NA),
  "Generalised hate" = lapply(directed_results,
    function(x) if (!is.null(x$generalised)) round(fixef(x$generalised)["MoralWords"], 4) else NA)
)

summary_df <- do.call(rbind, lapply(names(checks), function(check_name) {
  data.frame(
    Check       = check_name,
    Politicians = checks[[check_name]][["Politicians"]],
    Newspeople  = checks[[check_name]][["Newspeople"]],
    Activists   = checks[[check_name]][["Activists"]],
    stringsAsFactors = FALSE
  )
}))

print(summary_df, row.names = FALSE, digits = 4)

cat("\nOut-of-sample R² improvement (moral vs content model):\n")
for (nm in datasets) {
  r2_df <- oos_r2_results[[nm]]
  ratio <- r2_df$Moral_vs_Content_ratio[
    r2_df$Specification == "Author + Content + Moral"
  ]
  cat(" ", nm, ":", round(ratio, 3), "x",
      "(paper reported:", c("1.22x", "1.55x", "1.42x")[match(nm, datasets)], ")\n")
}

cat("\n", rep("=", 55), "\n", sep = "")
cat("ALL SUPPLEMENT ANALYSES COMPLETE\n")
cat(rep("=", 55), "\n", sep = "")

save.image("supplements_workspace.RData")
cat("Full workspace saved.\n")
```

# Generate Visualizations

## Robustness Check Coefficient Stability Plot

```{r}
robustness_sources <- list()

robustness_sources$main <- imap_dfr(bb_models, function(m, nm) {
  data.frame(Dataset = nm, Check = "Main model (BB)",
             Estimate = fixef(m)$cond["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_sources$source_hate <- imap_dfr(source_hate_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  data.frame(Dataset = nm, Check = "Source hate control",
             Estimate = fixef(m)["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_sources$binary <- imap_dfr(binary_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  coefs <- fixef(m)
  val   <- if ("MoralBinaryTRUE" %in% names(coefs)) coefs["MoralBinaryTRUE"] else NA
  data.frame(Dataset = nm, Check = "Binary indicator",
             Estimate = val, stringsAsFactors = FALSE)
})

robustness_sources$proportions <- imap_dfr(proportions_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  coefs <- fixef(m)
  val   <- if ("MoralWordsProp" %in% names(coefs)) coefs["MoralWordsProp"] else NA
  data.frame(Dataset = nm, Check = "Word proportions",
             Estimate = val, stringsAsFactors = FALSE)
})

if (exists("directed_results")) {
  robustness_sources$directed <- imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$directed)) return(NULL)
    data.frame(Dataset = nm, Check = "Directed hate",
               Estimate = fixef(x$directed)["MoralWords"],
               stringsAsFactors = FALSE)
  })
  robustness_sources$generalised <- imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$generalised)) return(NULL)
    data.frame(Dataset = nm, Check = "Generalised hate",
               Estimate = fixef(x$generalised)["MoralWords"],
               stringsAsFactors = FALSE)
  })
} else {
  cat("Note: directed_results not found - skipping directed/generalised hate checks.\n")
}

robustness_sources$interactions <- imap_dfr(interaction_results, function(m, nm) {
  if (is.null(m)) return(NULL)
  data.frame(Dataset = nm, Check = "With interactions",
             Estimate = fixef(m)["MoralWords"],
             stringsAsFactors = FALSE)
})

robustness_data <- bind_rows(robustness_sources) %>%
  filter(!is.na(Estimate)) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Check   = factor(Check,   levels = unique(Check))
  )


robustness_data <- bind_rows(
  # Main model coefficients from BB
  imap_dfr(bb_models, function(m, nm) {
    data.frame(
      Dataset = nm, Check = "Main model (BB)",
      Estimate = fixef(m)$cond["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Source hate control
  imap_dfr(source_hate_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Source hate control",
      Estimate = fixef(m)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Binary indicator
  imap_dfr(binary_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    coefs <- fixef(m)
    val   <- if ("MoralBinaryTRUE" %in% names(coefs)) coefs["MoralBinaryTRUE"] else NA
    data.frame(
      Dataset = nm, Check = "Binary indicator",
      Estimate = val,
      stringsAsFactors = FALSE
    )
  }),
  # Proportions
  imap_dfr(proportions_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    coefs <- fixef(m)
    val   <- if ("MoralWordsProp" %in% names(coefs)) coefs["MoralWordsProp"] else NA
    data.frame(
      Dataset = nm, Check = "Word proportions",
      Estimate = val,
      stringsAsFactors = FALSE
    )
  }),
  # Directed hate
  imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$directed)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Directed hate",
      Estimate = fixef(x$directed)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Generalised hate
  imap_dfr(directed_results, function(x, nm) {
    if (is.null(x$generalised)) return(NULL)
    data.frame(
      Dataset = nm, Check = "Generalised hate",
      Estimate = fixef(x$generalised)["MoralWords"],
      stringsAsFactors = FALSE
    )
  }),
  # Interactions
  imap_dfr(interaction_results, function(m, nm) {
    if (is.null(m)) return(NULL)
    data.frame(
      Dataset = nm, Check = "With interactions",
      Estimate = fixef(m)["MoralWords"],
      stringsAsFactors = FALSE
    )
  })
) %>%
  filter(!is.na(Estimate)) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Check   = factor(Check,   levels = c("Main model (BB)", "Source hate control",
                                          "Binary indicator", "Word proportions",
                                          "Directed hate", "Generalised hate",
                                          "With interactions"))
  )

p_robust <- ggplot(robustness_data,
                   aes(x = Check, y = Estimate, color = Dataset, group = Dataset)) +
  geom_hline(yintercept = 0, color = "grey50", linetype = "dashed") +
  geom_line(size = 0.8, alpha = 0.6) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_manual(values = wes_palette("Darjeeling1")[c(1, 2, 3)]) +
  labs(
    title    = "MoralWords Coefficient Across Robustness Specifications",
    subtitle = "Positive values across all checks confirm robustness of the main finding",
    x        = NULL,
    y        = "MoralWords Coefficient Estimate",
    color    = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 10),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_robust)
ggsave(paste0(graphPath, "Robustness_MoralWords.pdf"),
       p_robust, width = 20, height = 10, units = "cm", scale = 1.2)
```

## Out-of-Sample R-Squared Improvement Table

```{r}
r2_improve_data <- bind_rows(
  imap_dfr(oos_r2_results, function(df, nm) {
    ratio <- df$Moral_vs_Content_ratio[
      df$Specification == "Author + Content + Moral"
    ]
    data.frame(Dataset = nm, Source = "Our replication",
               Ratio = ratio, stringsAsFactors = FALSE)
  }),
  data.frame(
    Dataset = c("Politicians", "Newspeople", "Activists"),
    Source  = "Parent paper",
    Ratio   = c(1.22, 1.55, 1.42),
    stringsAsFactors = FALSE
  )
) %>%
  mutate(
    Dataset = factor(Dataset, levels = c("Politicians", "Newspeople", "Activists")),
    Source  = factor(Source,  levels = c("Parent paper", "Our replication"))
  )

p_r2 <- ggplot(r2_improve_data,
               aes(x = Dataset, y = Ratio, fill = Source)) +
  geom_col(position = position_dodge(width = 0.6),
           width = 0.5, color = "white") +
  geom_hline(yintercept = 1, color = "grey40", linetype = "dashed") +
  scale_fill_manual(values = c("Parent paper"    = "grey60",
                               "Our replication" = "steelblue")) +
  scale_y_continuous(breaks = seq(0, 2.5, by = 0.5),
                     limits = c(0, 2.7)) +
  labs(
    title    = "Out-of-Sample R² Improvement from Adding Moral Language",
    subtitle = "Ratio of moral language model R² to content-only model R²\nDashed line at 1.0 = no improvement",
    x        = NULL,
    y        = "R² Improvement Ratio",
    fill     = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "top",
    axis.text       = element_text(size = 11),
    plot.title      = element_text(size = 13, face = "bold"),
    plot.subtitle   = element_text(size = 10, color = "grey40")
  )

print(p_r2)
ggsave(paste0(graphPath, "OOS_R2_improvement.pdf"),
       p_r2, width = 16, height = 10, units = "cm", scale = 1.2)
```